Efficient, Robust and Exact Boolean Operations on N Triangular Mesh Primitives

### 2016-10-16 summary.tex
10.17
Signed-off-by: RUI WANG <RUI WANG>

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{falseclass}
\caption{In a 2D view, face $\bm{s}$ is on the surface of mesh $P$. However, because we use barycenter $v_c(\bm{s})$ to compute the indicator  and the coordinates of $v_c(\bm{s})$ contain round-off error, we might falsely classify $\bm{s}$ as outside of $P$.}
\label{fig:falseclass}
\end{figure}

@@

\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.2in]{p-reps}
%\caption{Plane-based representation of triangle}
\end{wrapfigure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=2in]{pbi}
\caption{Triangle $t_1$ and $t_2$ are from mesh $P_i, P_j$ respectively. They intersect on line segment, generating intersection $\bm{\mathcal{I}}_{12}$ on $t_1$ and $\bm{\mathcal{I}}_{21}$ on $t_2$. The PBI-rep of $\bm{\mathcal{I}}_{12}$ is $\{t_1, \bm{p}_{t_2, sp}, (\bm{p}_{t_2, b}^0, \bm{p}_{t_2, b}^1),\{(P_i, \Psi_i), (P_j, \Psi_j)\}\}$.}
\label{fig:pbi}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{twin}
\caption{Six situations of edge intersections. The first three subgraphs are edge-face intersections. The last three ones are edge-edge intersections. (a) Triangles are located in two sides, cross condition. (b) Triangles are located in the same sides, invalid condition. (c) One of the triangles are coplanar, coplanar condition. (d) Double twin intersections, cross condition. (e) Double twin intersections, coplanar condition. (f) Double twin intersections, coplanar condition.}
\label{fig:twin}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=2.5in]{falseclass}
\caption{In a 2D view, face $\bm{s}$ from $P_2$ is on the surface of mesh $P_1$. However, because we use face barycenter $\bm{v}_c$ to compute the indicator, the coordinates of $\bm{v}_c$ contain round-off error and move to $\bm{v}'_c$, we might falsely classify $\bm{s}$ as outside of $P_2$.}
\label{fig:falseclass}
\end{figure}

@@

\begin{wrapfigure}{r}[0in]{0in}
\includegraphics[width=1.5 in]{p-reps}
%\caption{Plane-based representation of triangle}
\end{wrapfigure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{pbirep}
\caption{Triangle $t_1$ and $t_2$ are from mesh $P_i, P_j$ respectively. They intersect on line segment, generating intersection $\bm{\mathcal{I}}_{12}$ on $t_1$ and $\bm{\mathcal{I}}_{21}$ on $t_2$. The PBI-rep of $\bm{\mathcal{I}}_{12}$ is $\{t_1, \bm{p}_{t_2, sp}, (\bm{p}_{t_2, b}^0, \bm{p}_{t_2, b}^1),\{(P_i, \Psi_i), (P_j, \Psi_j)\}\}$.}
\label{fig:pbi}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=3.5in]{edgeisect}
\caption{Six situations of edge interse ctions. The first three subgraphs are edge-face intersections. The last three ones are edge-edge intersections. (a) Triangles are located in two sides, cross condition. (b) Triangles are located in the same sides, invalid condition. (c) One of the triangles are coplanar, coplanar condition. (d) Double twin intersections, cross condition. (e) Double twin intersections, coplanar condition. (f) Double twin intersections, coplanar condition.}
\label{fig:twin}
\end{figure}
